\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-05-08 ZpL/ZpL.tex
Remark on the correctness

Unfortunately, automatically checking the assumptions of Proposition 
\ref{prop:precision} in full generality is difficult because it requires bounds
on higher derivatives.  To produce provably correct results, the assumptions
can be checked by hand \cite{caruso-roe-vaccon:14a, caruso:2017, LV16},
or \ZpCR may be used.
\todo{NDXavier: I would not mention \ZpCR here but say instead that we
can use \cite[Proposition~3.12]{caruso-roe-vaccon:14a} and that we plan
to include this in a next release of the package.}

>>>>

Unfortunately, automatically checking the assumptions of Proposition 
\ref{prop:precision} in full generality is not straightforward because 
it requires bounds on higher derivatives. For now, our package does not 
perform this inspection but we plan to include it in a forthcoming 
release, along the lines of 
\cite[Proposition~3.12]{caruso-roe-vaccon:14a}. 
Meanwhile, the assumptions can be checked by hand using the results
of \cite{caruso-roe-vaccon:14a, caruso:2017, LV16}.
